Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\extraspacing {\underline{\em Example 5.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_2)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \qed

@@

\extraspacing {\underline{\em Example 5.3.}} Consider tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$ of $ \J(R_1, H', V)$ given in Example 5.2. For $\bm{t}_1 = (\alpha, h_2', v_1)$, its effective horizontal segment is $\texttt{DC}$ (see Figure~\ref{fig:hv:type2:ex}b. For $\bm{t}_2 = (\alpha, h_3', v_1)$, its effective horizontal segment is \texttt{EB}. For $\bm{t}_2 = (\alpha, h_3', v_2) \in \J(R_1, H', V)$, its effective horizontal segment is \texttt{EA}.
\vgap

@@

@@

\input{appB.tex}

@@

@@

@@

@@

@@

@@

@@

>>>>

\extraspacing {\underline{\em Example 5.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \qed

@@

\extraspacing {\underline{\em Example 5.3.}} Consider the tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$ of $ \J(R_1, H', V)$ given in Example 5.2. For $\bm{t}_1 = (\alpha, h_2', v_1)$, its effective horizontal segment is $\texttt{DC}$ (see Figure~\ref{fig:hv:type2:ex}b). For $\bm{t}_2 = (\alpha, h_3', v_1)$, its effective horizontal segment is \texttt{EB}. For $\bm{t}_3 = (\alpha, h_3', v_2) \in \J(R_1, H', V)$, its effective horizontal segment is \texttt{EA}. Accordingly, as can be seen from Figure~\ref{fig:hv:type2:ex}c,
$\contained_{R_{k-2}}(\bm{t}_1) = \contained_{R_2}(\bm{t}_1) = \set{\beta_1}$, $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, and $\contained_{R_2}(\bm{t}_2) = \set{\beta_3}$.
\qed

@@

\extraspacing {\underline{\em Example 5.4.}} For $\bm{t}_1 = (\alpha, h_2', v_1)$, first find the full segment of $h_2'$, which is $h_2$. As $\beta_1$ is the only rectangle in $\contained_{R_2}(\bm{t}_1)$, Line 5 adds tuple $(\alpha, \beta_1, h_2, v_1)$ to $\J_2$. For $\bm{t}_2 = (\alpha, h_3', v_2)$, the full segment of $h_3'$ is $h_3$. As $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, Line 5 adds $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_2)$, and $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$. Finally, the processing of $\tm{t}_3 = (\alpha, h_3', v_2)$ adds $(\alpha, \beta_3, h_3, v_2)$ to $\J_2$.
\qed

@@

\input{4.1.tex}

@@

\input{4.2.tex}

@@

\input{4-comp.tex}

@@

\input{4.3.tex}

@@

\input{5.1.tex}

@@

\input{5.2.tex}

@@

\input{5-comp.tex}

@@

\input{5.3.tex}
